\hypertarget{namespaceFragments}{}\section{Fragments Namespace Reference}
\label{namespaceFragments}\index{Fragments@{Fragments}}


Constructs a \mbox{\hyperlink{classQRail_1_1Fragments_1_1Factory}{Q\+Rail\+::\+Fragments\+::\+Factory}} to generate Linked Connections fragments on the fly.  




\subsection{Detailed Description}
Constructs a \mbox{\hyperlink{classQRail_1_1Fragments_1_1Factory}{Q\+Rail\+::\+Fragments\+::\+Factory}} to generate Linked Connections fragments on the fly. 

Sets the list of fragments associated with this page to the given Q\+List$<$\+Fragment $\ast$$>$ \&fragments.

Gets the list of fragments associated with this page and return it.

Sets the U\+RI of the linked connection previous page to the given Q\+Url \&hydra\+Previous.

Retrieves the U\+RI of the previous linked connection page and returns it.

Sets the U\+RI of the linked connection next page to the given Q\+Url \&hydra\+Previous.

Retrieves the U\+RI of the next linked connection page and returns it.

Sets the timestamp of the linked connection fragment to the given Q\+Date\+Time \&timestamp.

Retrieves the timestamp of the linked connection page and returns it.

Sets the U\+RI of the linked connection page to the given Q\+Url \&uri.

Retrieves the U\+RI of the linked connection page and returns it.

Constructs a Page to store the information about a Linked Connection page for the Connection Scan Algorithm (C\+SA).

Sets the direction of the vehicle in this linked connection fragment to the given Q\+String \&direction.

Retrieves the direction of the vehicle in this linked connection fragment and returns it.

Sets the route U\+RI of the linked connection fragment to the given Q\+Url \&route\+U\+RI.

Retrieves the route U\+RI of the linked connection fragment and returns it.

Sets the trip U\+RI of the linked connection fragment to the given Q\+Url \&trip\+U\+RI.

Retrieves the trip U\+RI of the linked connection fragment and returns it.

Sets the arrival delay (in seconds) of the linked connection fragment to the given qint16 \&arrival\+Delay.

Retrieves the arrival delay (in seconds) of the linked connection fragment and returns it.

Sets the departure delay (in seconds) of the linked connection fragment to the given qint16 \&departure\+Delay.

Retrieves the departure delay (in seconds) of the linked connection fragment and returns it.

Sets the arrival time of the linked connection fragment to the given Q\+Date\+Time \&arrival\+Time.

Retrieves the arrival time of the linked connection fragment and returns it.

Sets the departure time of the linked connection fragment to the given Q\+Date\+Time \&departure\+Time.

Retrieves the departure time of the linked connection fragment and returns it.

Sets the arrival station U\+RI of the linked connection fragment to the given Q\+Url \&arrival\+Station\+U\+RI.

Retrieves the arrival station U\+RI of the linked connection fragment and returns it.

Sets the departure station U\+RI of the linked connection fragment to the given Q\+Url \&departure\+Station\+U\+RI.

Retrieves the departure station U\+RI of the linked connection fragment and returns it.

Sets the U\+RI of the linked connection fragment to the given Q\+Url \&uri.

Retrieves the U\+RI of the linked connection fragment and returns it.

Constructs a Fragment to store the information about a Linked Connection fragment for the Connection Scan Algorithm (C\+SA).

Sets the \mbox{\hyperlink{classQRail_1_1Network_1_1Manager}{Q\+Rail\+::\+Network\+::\+Manager}} instance to the given \mbox{\hyperlink{classQRail_1_1Network_1_1Manager}{Q\+Rail\+::\+Network\+::\+Manager}} $\ast$http.

Gets the \mbox{\hyperlink{classQRail_1_1Network_1_1Manager}{Q\+Rail\+::\+Network\+::\+Manager}} instance and returns it.

Reads the network reply, parses it using the helper methods.

Converts the J\+S\+O\+N-\/\+LD into a Q\+Rail\+::\+Fragments\+::\+Fragments object and returns it.

Sends a request to the \mbox{\hyperlink{classQRail_1_1Network_1_1Manager}{Q\+Rail\+::\+Network\+::\+Manager}} to retrieve a Linked Connections page by U\+RI.

Starts the generation process of a \mbox{\hyperlink{classQRail_1_1Fragments_1_1Page}{Q\+Rail\+::\+Fragments\+::\+Page}} object by requesting a page by departure time.

Starts the generation process of a \mbox{\hyperlink{classQRail_1_1Fragments_1_1Page}{Q\+Rail\+::\+Fragments\+::\+Page}} object by requesting a page by U\+RI.

Constructs a \mbox{\hyperlink{classQRail_1_1Fragments_1_1Factory}{Q\+Rail\+::\+Fragments\+::\+Factory}} if none exists and returns the instance.

When the page is ready, the page\+Ready signal will be emitted.

When the reply is completed parsed and no errors were encountered, the page\+Ready signal is emitted. In case we faced an error, the error signal is emitted with an error message.

Emits the uri\+Changed signal.

Emits the departure\+Station\+U\+R\+I\+Changed signal.

Emits the arrival\+Station\+U\+R\+I\+Changed signal.

Emits the departure\+Time\+Changed signal.

Emits the arrival\+Time\+Changed signal.

Emits the departure\+Delay\+Changed signal.

Emits the arrival\+Delay\+Changed signal.

Emits the trip\+U\+R\+I\+Changed signal.

Emits the route\+U\+R\+I\+Changed signal.

Emits the direction\+Changed signal.

Emits the timestamp\+Changed signal.

Emits the hydra\+Previous\+Changed signal.

Emits the fragments\+Changed signal. 