\hypertarget{namespaceNetwork}{}\section{Network Namespace Reference}
\label{namespaceNetwork}\index{Network@{Network}}


Constructs a \mbox{\hyperlink{classQRail_1_1Network_1_1Manager}{Q\+Rail\+::\+Network\+::\+Manager}} facade to access the network using the H\+T\+TP protocol.  




\subsection{Detailed Description}
Constructs a \mbox{\hyperlink{classQRail_1_1Network_1_1Manager}{Q\+Rail\+::\+Network\+::\+Manager}} facade to access the network using the H\+T\+TP protocol. 

Sets the \mbox{\hyperlink{classQRail_1_1Network_1_1Dispatcher}{Q\+Rail\+::\+Network\+::\+Dispatcher}} instance.

Gets the \mbox{\hyperlink{classQRail_1_1Network_1_1Dispatcher}{Q\+Rail\+::\+Network\+::\+Dispatcher}} instance.

Sets the Q\+Abstract\+Network\+Cache instance.

Gets the Q\+Abstract\+Network\+Cache instance.

Sets the Q\+Network\+Access\+Manager instance.

Gets the Q\+Network\+Access\+Manager instance.

Changes the current accept header to the given Q\+String.

Retrieves the current accept header used to make requests in this H\+T\+TP instance.

Changes the current user agent to the given Q\+String.

Retrieves the current user agent used to make requests in this H\+T\+TP instance.

Everytime a H\+T\+TP request has been made by the user it needs several default headers to complete it\textquotesingle{}s mission.

Retrieves the headers of the resource from the given Q\+Url url using a H\+E\+AD request.

Deletes a certain resource from the given Q\+Url url using a D\+E\+L\+E\+TE request.

Posts data to a certain resource from the given Q\+Url url using a P\+O\+ST request.

Retrieves a certain resource from the given Q\+Url \&url using a G\+ET request.

Constructs a \mbox{\hyperlink{classQRail_1_1Network_1_1Manager}{Q\+Rail\+::\+Network\+::\+Manager}} if none exists and returns the instance.

The \mbox{\hyperlink{classQRail_1_1Network_1_1Manager}{Q\+Rail\+::\+Network\+::\+Manager}} facade makes network access in Qt abstract from the underlying library (Q\+Network\+Access\+Manager, lib\+Curl, ...).

The result as a Q\+Network\+Reply $\ast$reply will be available through the Qt event system. Implement the custom\+Event() method in your Q\+Object to receive the data.

The prepare\+Request method just does that, it adds the Accept, User-\/\+Agent header to the request and allows redirects. 