\hypertarget{namespaceVehicleEngine}{}\section{Vehicle\+Engine Namespace Reference}
\label{namespaceVehicleEngine}\index{VehicleEngine@{VehicleEngine}}


Constructs a \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Factory}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Factory}} to generate \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Vehicle}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Vehicle}} objects on the fly.  




\subsection{Detailed Description}
Constructs a \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Factory}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Factory}} to generate \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Vehicle}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Vehicle}} objects on the fly. 

Sets the intermediary stops of the vehicle to the given Q\+List$<$\+Q\+Rail\+::\+Vehicle\+Engine\+::\+Stop $\ast$$>$ \&intermediary\+Stops.

Gets the intermediary stops of the vehicle and returns it.

Sets the headsign of the vehicle to the given Q\+String \&headsign Emit the headsign\+Changed signal.

Gets the headsign of the vehicle and returns it.

Sets the U\+RI of the current trip to the given Q\+Url \&trip\+U\+RI Emit the trip\+U\+R\+I\+Changed signal.

Gets the U\+RI of the current trip and returns it.

Sets the U\+RI of the vehicle to the given Q\+Url \&uri Emit the uri\+Changed signal.

Gets the U\+RI of the vehicle and returns it.

Constructs a \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Vehicle}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Vehicle}} to store information about the vehicle itself with intermediary stops.

Constructs a \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Vehicle}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Vehicle}} to store information about the vehicle itself without intermediary stops.

Constructs a \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Vehicle}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Vehicle}} to store information about the vehicle itself.

Sets the is\+Extra\+Stop to the given bool \&is\+Extra\+Stop.

Gets the is\+Extra\+Stop and returns it.

Sets the type to the given \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Stop_af078938bc06ff906b6fc843d8c0206fa}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Stop\+::\+Type}} \&type Emits the type\+Changed signal.

Gets the type and returns it.

Sets the occupancy level for this stop to the given \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Stop_ad967ed81b19762bd582c1af07354a6d4}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Stop\+::\+Occupancy\+Level}} \&occupancy\+Level.

Gets the occupancy level and returns it.

Sets the is\+Arrival\+Canceled for this stop to the given bool \&is\+Arrival\+Canceled.

Gets the is\+Arrival\+Canceled and returns it.

Gets the arrival delay for this stop and returns it.

Sets the arrival time for this stop to the given Q\+Date\+Time \&arrival\+Time.

Gets the arrival time for this stop and returns it.

Sets the is\+Departure\+Canceled for this stop to the given bool \&is\+Departure\+Canceled.

Gets the is\+Departure\+Canceled and returns it.

Sets the departure delay for this stop to the given qint16 departure\+Delay.

Gets the departure delay for this stop and returns it.

Sets the departure time for this stop to the given Q\+Date\+Time \&departure\+Time.

Gets the departure time for this stop and returns it.

Sets the has\+Left to the given bool \&has\+Left.

Gets the has\+Left and returns it.

Sets the is\+Platform\+Normal to the given bool \&is\+Platform\+Normal.

Gets the is\+Platform\+Normal and returns it.

Sets the platform for this stop to the given Q\+String \&platform.

Gets the platform for this stop and returns it.

Sets the station for this stop to the given Station\+Engine\+::\+Station $\ast$station.

Gets the station for this stop and returns it.

Constructs a \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Stop}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Stop}} with the given parent.

Constructs a Vehicle\+Engine\+::\+Null\+Vehicle if none exists and returns the instance.

Constructs a \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1NullVehicle}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Null\+Vehicle}} according to the Null design pattern.

Sets the language to the given const Q\+Locale\+::\+Language \&language.

Gets the language and returns it.

Sets the Station\+Engine\+::\+Factory instance to the given Station\+Engine\+::\+Factory $\ast$station\+Factory.

Gets the Station\+Engine\+::\+Factory instance and returns it.

Sets the \mbox{\hyperlink{classQRail_1_1Network_1_1Manager}{Q\+Rail\+::\+Network\+::\+Manager}} instance to the given \mbox{\hyperlink{classQRail_1_1Network_1_1Manager}{Q\+Rail\+::\+Network\+::\+Manager}} $\ast$http.

Gets the \mbox{\hyperlink{classQRail_1_1Network_1_1Manager}{Q\+Rail\+::\+Network\+::\+Manager}} instance and returns it.

Strips the vehicle ID from the U\+RI and returns it.

Adds a vehicle to the cache.

Tries to fetch a vehicle from the cache.

Generates \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Stop_ad967ed81b19762bd582c1af07354a6d4}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Stop\+::\+Occupancy\+Level}} from J\+S\+O\+N-\/\+LD and returns it.

Generates \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Stop}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Stop}} from J\+S\+O\+N-\/\+LD and returns it.

Reads the Q\+Network\+Reply $\ast$reply and validates it before the processing begins.

Constructs a \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Factory}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Factory}} if none exists and returns the instance.

After the validation, the reply is processed and a \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Vehicle}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Vehicle}} is generated with it\textquotesingle{}s \mbox{\hyperlink{classQRail_1_1VehicleEngine_1_1Stop}{Q\+Rail\+::\+Vehicle\+Engine\+::\+Stop}} list.

In case the vehicle can\textquotesingle{}t be retrieved from the cache, a nullptr is returned.

In case the U\+RI of the vehicle already exists in the cache, the entry is updated with the new vehicle.

Emits the station\+Changed signal.

Emits the platform\+Changed signal.

Emits the is\+Platform\+Normal\+Changed signal.

Emits the has\+Left\+Changed signal.

Emits the departure\+Time\+Changed signal.

Emits the departure\+Delay\+Changed signal.

Emits the is\+Departure\+Canceled\+Changed signal.

Emits the arrival\+Time\+Changed signal.

Emits the arrival\+Delay\+Changed signal.

Emits the is\+Arrival\+Canceled\+Changed signal.

Emits the occupancy\+Level\+Changed signal.

Emits the is\+Extra\+Stop\+Changed signal.

Emit the intermediary\+Stops\+Changed signal. 